\documentclass[../MasterThesis.tex]{subfiles}
\graphicspath{ {./assets/images/} }


%----------------------------------------------------------------------------
%----------------------------------------------------------------------------

\begin{document}
	
	
	

%
%
%
%
%=======================================================================================================
%
%
%
%
%=======================================================================================================
% CHAPTER: SYSTEM REQUIREMENTS AND SPECIFICATIONS
%=======================================================================================================
\newpage
\section{System Requirements and Specifications} \label{section:systemrequirementsandspecifications}

%Define the overall goals and objectives of your project.
%Specify the functional and non-functional requirements of the system. This includes what the system is expected to do, its features, and any constraints it must adhere to.
%Outline any specific hardware or software requirements necessary for the project.
%Detail the methodologies or approaches you'll use for system development.



%-------------------------------------------------------------------------------------------------------
\subsection{User Requirements} \label{subsection:userrequirements}
% Identify and describe the requirements from the end-user perspective.




%Who are the primary users of the system?
%What are the main tasks or activities that users will perform using the system?
%What are the goals and objectives of the users when interacting with the system?
%What are the characteristics of the users, such as technical expertise, age, education level, etc.?
%What are the environmental considerations, such as the location and conditions in which the system will be used?
%Are there any regulatory or legal requirements that need to be considered regarding user interaction?
%What are the usability expectations or preferences of the users regarding interface design, navigation, etc.?
%Are there any accessibility requirements that need to be addressed for users with disabilities?
%Are there any cultural or language considerations that need to be accommodated for the users?












%-------------------------------------------------------------------------------------------------------
\subsection{Technical Requirements} \label{subsection:technicalrequirements}
% Detail the technical requirements for the system.


TODO Introduction to Section (?)

TODO Answer questions

\begin{itemize}

\item What are the hardware requirements for running the system, such as processor, memory, storage, etc.?

The system should be capable of running frontend development tools such as Yarn and executing applications within Docker containers.
While implementing, it was observed that the system should have a minimum of 16GB RAM to ensure smooth execution of the development environment and Docker containers.



\item What are the software requirements, including operating system compatibility, third-party libraries or frameworks, etc.?

While testing it seemed to not run on Windows. Because of this, a Linux system (Ubuntu 22.04) was used. Regarding the documentation in the README file, the Mac operating system should be able to run the code after making adjustments.


% \item Are there any performance requirements, such as response time, throughput, scalability, etc.?

\item What are the security requirements for protecting the system and its data from unauthorized access or breaches?

The Docker containers use a \textit{you snooze you lose} approach, where the container terminates automatically if there are no incoming requests within a certain time frame. 

In addition to this, the system adheres to standard security practices.




\item What are the data management requirements, including data storage, retrieval, backup, and retention policies?

\item Are there any legal or compliance requirements related to data privacy, intellectual property, etc.?

\item What are the maintenance and support requirements for the system, including updates, patches, user support, etc.?
	
\end{itemize}	
	
	
	
	
\end{document}