\documentclass[../MasterThesis.tex]{subfiles}
\graphicspath{ {./assets/images/} }


%----------------------------------------------------------------------------
%----------------------------------------------------------------------------

\begin{document}
	
	

%---------------------------------------------------------------------------
\newpage
%---------------------------------------------------------------------------

\section{Technical Background} \label{section:technicalbackground}


In this Chapter, the structure and usage of the MLT framework is explained and a brief overview of video streaming components and additional components is given. Furthermore, protocol buffers are introduced and explained with examples.


%---------------------------------
\subsection{MLT} \label{subsection:melt}

The MLT framework is a multimedia framework that can be used for video editing and playback. It is written in C and provides a set of tools, libraries and services for handling multimedia content, including video and audio. Melt is the name of the command line tool, which exposes various functionality of the framework and was developed for testing the MLT framework~\cite{melt}. 




A variety of multimedia tasks can be performed with MLT, including video editing, rendering, the application of filters on audio or video files and converting data between different formats.
The areas of applications include film production, television broadcasting and digital content creation. 
Additionally, the MLT framework supports a wide range of media formats and codecs.




\subsubsection*{Structure of the MLT framework}


In the following, the relevant components of the MLT framework's structure will be explained. This is based on the documentation as well as the code of the framework~\cite{melt, melt_code}.
%
\textit{Producer}, \textit{Consumer} and \textit{MLT frame objects} are fundamental components in the MLT framework.

A \textit{MLT frame object} is a data structure that is used for representing multimedia content. 
It is a container that holds multimedia data. Each \textit{MLT frame object} contains a single uncompressed frame image and its associated audio samples. These frame objects can be processed individually, which allows the user to manipulate and transform multimedia content efficiently.
\textit{MLT frame objects} can store the multimedia data in various formats and they support metadata annotations, which allows to attach additional information or properties to the multimedia content. This includes filters for manipulating the content, which are discussed in Section~\ref{subsection:meltfilter}.


A \textit{Producer} generates or provides data -- it produces the \textit{MLT frame objects}. 
It reads data from files or other data sources. The \textit{Producer} serves as the starting point of the data processing pipeline. It retrieves the raw data and passes it on to other components, for example the \textit{Consumer}. This can be seen in Figure~\ref{fig:producer_consumer}.

A \textit{Consumer} requests \textit{MLT frame objects} from the \textit{Producer}.
It is responsible for consuming or processing the data that was produced by the \textit{Producer} or other components that are between the \textit{Producer} and \textit{Consumer}. 
The \textit{Consumer} represents the endpoint of the data processing pipeline and produces the final output or results.



\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		% Nodes
		\node[draw, rectangle] (producer) at (0,0) {Producer};
		\node[draw, rectangle] (consumer) at (3,0) {Consumer};
		% Arrows
		\draw[->,>=stealth, line width=1.2pt] (producer) -- (consumer);
	\end{tikzpicture}
	\caption{Producer-Consumer Relationship in the MLT framework.}
	\label{fig:producer_consumer}
\end{figure}

Applying filters in the MLT framework is a technique for manipulating multimedia content, including videos. 
MLT filters can perform a wide range of visual and audio operations, including colour correction, blurring, sharpening, cropping and resizing. A list of the filters can be found on the MLT website and example applications of a wide selection of visual filters can be seen in Appendix~\ref{appendix:differentMeltFilter}~\cite{melt_filters}.


To apply a filter in Melt, a filter instance has to be created. The filter instance has to contain the name of the filter and, if applicable, the filter parameters with corresponding values.
Filters are processing units that manipulate the multimedia data as it flows through the data processing pipeline. They are placed between the producer and consumer, allowing them to modify the data before it reaches the consumer. A MLT data processing pipeline containing a filter is shown in Figure~\ref{fig:producer_filter_consumer}.



\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		% Nodes
		\node[draw, rectangle] (producer) at (0,0) {Producer};
		\node[draw, rectangle] (filter) at (3,0) {Filter};
		\node[draw, rectangle] (consumer) at (6,0) {Consumer};
		% Arrows
		\draw[->,>=stealth, line width=1.2pt] (producer) -- (filter);
		\draw[->,>=stealth, line width=1.2pt] (filter) -- (consumer);
	\end{tikzpicture}
	\caption{Producer-Filter-Consumer Relationship in the MLT framework.}
	\label{fig:producer_filter_consumer}
\end{figure}



\subsubsection*{Usage of the MLT framework}

In this Section, the usage of the Melt framework is explained with code examples. The function of each code segment is explained.
This is based on the implemented code for this project, the code of the MLT framework and the MLT documentation~\cite{melt_code, melt}.

The code structure described below refers to the creation of the necessary MLT components to apply a filter.


\begin{description}[font=\color{RedViolet!80!black}, style=nextline]
	
	%-----------------------------------------------
	\item[Initialise the factory] 
	
	This command initialises the MLT factory, to set up the environment for creating and managing multimedia objects.
	
	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_factory_init(const char * directory); \end{lstlisting}

	The function takes a directory path as an optional parameter. In this directory, custom modules can be stored, which can then override the default settings. % and the \texttt{MLT\_REPOSITORY} environment variable. 
	
	
	%-----------------------------------------------	
	\item[Create a profile]
	
	In this line, a multimedia profile is created to define the video properties.
	
	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_profile profile = mlt_service_profile(mlt_service self); \end{lstlisting}
	
	The function \texttt{mlt\_service\_profile()} retrieves the profile that is associated with a given service. It takes a service as a parameter and returns its profile.
	
	


	%-----------------------------------------------	
	\item[Create a producer] 

	In this command, a producer object is created. The producer object generates or provides the data.

	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_producer producer = mlt_factory_producer(mlt_profile profile,
																							const char* service,
																							const void* resource); \end{lstlisting}
																						 
	The function \texttt{mlt\_factory\_producer()} creates a producer based on the profile, service and resources, which are the parameters of this function.


	
	
	%-----------------------------------------------	
	\item[Create properties] 
	
	
	This line retrieves the properties associated with a specified producer parameter within a property object.
	
	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_properties properties = MLT_PRODUCER_PROPERTIES(producer); \end{lstlisting}
	
	The macro \texttt{MLT\_PRODUCER\_PROPERTIES} internally accesses the properties of the producer.
	
	
	
	%-----------------------------------------------	
	\item[Create a consumer] 
	
	This line creates a consumer object that processes the data.
	
	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_consumer consumer = mlt_factory_consumer(mlt_profile profile, 
																							const char* service, 
																							const void* input); \end{lstlisting}
																
	The function \texttt{mlt\_factory\_consumer()} creates a consumer object based on the provided parameter profile, service and optional input. If the service object is not specified, it defaults to \texttt{MLT\_CONSUMER}.
											
																
	% TODO: seems to take properties as first parameter in codemill code? Is property and prfile the same?
	
	
	
	%-----------------------------------------------
	\item[Create a filter] 
	
	In this command a filter is created. The name of the filter is given as an argument in form of a string.
	
	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_filter filter = mlt_factory_filter(mlt_profile profile, 
																						const char* service, 
																						const void* input); \end{lstlisting}
														
	The \texttt{mlt\_factory\_filter()} function retrieves a filter based on the parameters. Those are the profile, the name of the filter as service and an optional argument of the filter.



	%-----------------------------------------------
	\item[Create and set filter properties] 

	This code creates a property object and sets the filter properties.

	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_properties filter_properties = mlt_filter_properties(filter); \end{lstlisting}

	The function \texttt{mlt\_filter\_properties()} retrieves the properties of a filter. The filter is given as a parameter.

	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_properties_set(mlt_properties self, 
													const char* name, 
													const char* value); \end{lstlisting}

	The function \texttt{mlt\_properties\_set()} assigns a new value to a property, in this case to a filter. The parameters are the filter properties, that were retrieved in the previous step, and the filter parameters and associated values as strings.
	
	
	
	
	%-----------------------------------------------
	\item[Connect elements] 
	
	The filter is connected to the producer and the consumer to the filter, if a filter is applied.
	
	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_filter_connect(mlt_filter self, mlt_service producer, int index); \end{lstlisting}

	The function \texttt{mlt\_filter\_connect} takes the filter and the producer as parameters and connects them.
	
	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_consumer_connect(mlt_consumer self, mlt_service producer); \end{lstlisting}

	The function \texttt{mlt\_filter\_connect} takes the consumer and the filter as parameters and connects them.
	
	
	If no filter is applied, the producer is being connected to the consumer directly.
	
	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_consumer_connect(mlt_consumer self,	mlt_service producer); \end{lstlisting}
	
	The function \texttt{mlt\_filter\_connect} takes the consumer and the producer as parameters and connects them.
	
	
	%-----------------------------------------------
	\item[Start consumer] 
	
	This line starts the consumer.
	
	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_consumer_start(mlt_consumer self);	\end{lstlisting}

	The function \texttt{mlt\_consumer\_start()} initiates the consumer in the MLT framework. It takes the consumer object as a parameter. 
	
	
	
	
	
	%-----------------------------------------------
	\item[Close the components]
	
	The following functions are responsible for closing the associated component within the MLT framework. These functions mark the end of a MLT process by closing and cleaning up resources.
	
	\begin{lstlisting}[language=C, numbers=none, columns=fullflexible, belowskip=0pt, aboveskip=9pt]
	mlt_consumer_close(mlt_consumer self); 
	mlt_producer_close(mlt_producer self); 
	mlt_profile_close(mlt_profile profile); 
	mlt_factory_close();\end{lstlisting}
	
	
\end{description}










%-------------------------------------------------------------------------------------------------------
%-------------------------------------------------------------------------------------------------------
\subsection{Overview of Video Streaming Components}
\label{subsection_OverviewVideoStreamingComponents}

In this Section, an overview of video streaming components that are relevant for this thesis project is given.

Transcoding is the conversion of one digital data format into another.
One form of video transcoding is the compression of videos with h.264:
The video compression standard h.264 can be used to compress and decompress video streams in the context of real-time communication~\cite{transcoding, h264}.
%	
File formats such as Audio Video Interleave (AVI) often serve as input files for video transcoding processes.
AVI can contain audio and video information to allow synchronised playback of audio and video components. 
It is a container format, which means that it can contain multiple streams of audio and video data, along with other multimedia data such as subtitles.
AVI files can undergo transcoding to optimise their compression, compatibility or quality, with h.264 being a commonly used codec for such purposes~\cite{avi, h264}.


WebRTC, is a free, open-source project for real-time communication between web browsers and other applications that was developed by Google in 2011. It enables direct peer-to-peer (P2P) communication without the need for intermediary servers.
WebRTC supports various video codecs, including h.264, which is used for video conferencing, streaming and other real-time applications. This means, that the video streams exchanged between the browser and the backend are encoded and decoded using h.264~\cite{webrtc, h264}.





%-------------------------------------------------------------------------------------------------------
%\subsubsection*{Named Pipe} 

%A named pipe is a type of interprocess communication (IPC) mechanism. It provides a way for processes to pass data to each other and it is bidirectional. 
%Named pipes follow a First-In-First-Out (FIFO) structure: The first data written into the pipe is the first data to be read. This maintains a sequential order for data transmission.
%A traditional pipe is \textit{unnamed} and terminates when its process terminates. A named pipe can last beyond the life of the process, as long as the system is running.~\cite{namedpipe}





%-------------------------------------------------------------------------------------------------------
%\subsubsection*{REST} 


Representational State Transfer (REST) is an architecture for network applications. A REST Application Programming Interface (API) exposes a set of endpoints, which are Uniform Resource Locators (URLs) that serve as addresses for communication between different software systems over the internet using hypertext transfer protocol (HTTP) methods~\cite{IEEE_Rest, webservice, Nodejs_Rest}.



	
JIT or Just-In-Time in the context of video streaming refers to a dynamic software solution employed for real-time video transformation. 
It is used for on-the-fly conversion of video files, optimising them for streaming. The process includes the transcoding of a video file, potentially one with non-web-friendly formats, into a more suitable format for the playback in web browsers.
JIT operates by dynamically preprocessing video content as it is requested by users. This is in contrast to the common technique of pre-converting video files into formats that are suitable for streaming or browsers in advance. 
This approach allows for greater flexibility and efficiency, as it minimises the need for storage space and allows real-time adjustment such as the adjustment of the RGB colours that is implemented and described in this thesis project.
Additionally, JIT allows to adjust video resolution, bitrate and other parameters in real-time to adapt the results to the user's bandwidth~\cite{JIT_IEEE}.







%-------------------------------------------------------------------------------------------------------
\subsection{Overview of Additional Components}
\label{subsection:overview_additional_components}


This Section introduces additional components that are relevant for this thesis project.


Docker is a platform that provides an isolated environment where applications can run. It enables the usage of these isolated environments, that are called containers.
Those Docker containers can reduce the problems that arise from environmental discrepancies. Docker enables testing in local environments while enhancing the reliability and comparability~\cite{docker}.



Node.js is a JavaScript (JS) runtime environment that enables the execution of JavaScript code outside of a web browser.
It enables developers to use JavaScript both on the client and server sides of web applications. 
Node.js has an open-source community that contributes to its evolution. This community-driven development model has led to a big selection of modules and libraries~\cite{nodejs, RM_Frontend, ap3_docs}.
%
To manage project dependencies and packages for Node.js, package managers such as Yarn or Node Package Manager (npm) can be used. These package managers allow developers to install, update and manage libraries and tools used in projects by providing a centralised repository of libraries and tools~\cite{RM_Frontend, npmyarn}.



Web services are software systems for communication between different applications over a network. 
They allow data exchange and function execution across platforms and programming languages. 
Java-based web services are commonly used in modern software development, due to the robustness and scalability of the Java platform for building distributed systems over the web.
Web services enable machine-to-machine (M2M) interaction -- the communication and data exchange between devices or systems~\cite{webservice}.

KDEN Live is a video editing software, that offers a wide range of features such as cutting, trimming and arranging video clips and adding effects, transitions and titles to videos. It also supports various file formats. KDEN Live is freely available, open-source and uses the MLT framework as its backend~\cite{kdenlive}.











%-------------------------------------------------------------------------------------------------------
\subsection{Protocol Buffer}
\label{subsection:protocolbuffer}


Protocol buffers are a binary data format developed by Google to compress data for sending it efficiently over a network. The structure of this format is defined in a \texttt{.proto} file. The \texttt{.proto} files are used to generate code for reading and writing to the protocol buffer~\cite{protobuffer}.



In this project, protocol buffers version 2 (proto2) were used. In the first line of the \texttt{.proto} file, the syntax is defined with the proto version that is being used. As an example, the syntax for proto2 is shown below.

\begin{lstlisting}[style=protobufStyle, numbers=none]
	syntax = "proto2";
\end{lstlisting}

\begin{description}[font=\normalfont\color{RedViolet!80!black}, style=nextline]
	

%---------------------------------------------------------------------------------------------------------
\item[Messages and Fields] 

Data structures are defined using message declarations. Messages can contain fields for the data, each with a unique identifier and a specified data type. The data types for proto2 are listed in Table~\ref{table:proto2_data_types}~\cite{proto2_doc}.

In the following, an example message is shown and described.
The example message represents a person's information, including their name, age and email address. This is defined as follows:

\begin{lstlisting}[style=protobufStyle, numbers=none]
	message Person {
		required string name = 1;
		required int32 age = 2;
		optional string email = 3;
	}
\end{lstlisting}

Person is the label of the message and name, age and email are the fields of the message with the data types \texttt{string} and \texttt{int32}.
The keywords \texttt{required} and \texttt{optional} define whether the field is mandatory or optional.
The numbers $1$, $2$ and $3$ are the fields' unique identifiers.


\begin{table}[H]
	\centering
	% \small % Adjusting font size
	% \renewcommand{\arraystretch}{0.75} % Adjusting row spacing
	\begin{tabular}{ll}
		\toprule
		\textbf{Data Type} & \textbf{Description} \\
		\midrule
		double & Double-precision floating-point number \\
		float & Single-precision floating-point number \\
		int32 & Signed 32-bit integer \\
		int64 & Signed 64-bit integer \\
		uint32 & Unsigned 32-bit integer \\
		uint64 & Unsigned 64-bit integer \\
		sint32 & Signed 32-bit integer (suitable for negative numbers) \\
		sint64 & Signed 64-bit integer (suitable for negative numbers) \\
		fixed32 & Unsigned 32-bit integer (four bytes) \\
		fixed64 & Unsigned 64-bit integer (eight bytes) \\
		sfixed32 & Signed 32-bit integer (four bytes) \\
		sfixed64 & Signed 64-bit integer (eight bytes) \\
		bool & Boolean value (true or false) \\
		string & Variable-length text string \\
		bytes & Variable-length sequence of bytes \\
		\bottomrule
	\end{tabular}
	\caption[Data types for fields in protocol buffers (proto2).]{Data types for fields in protocol buffers (proto2)~\cite{proto2_doc}.}
	\label{table:proto2_data_types}
\end{table}




%---------------------------------------------------------------------------------------------------------
\item[Enums] 

Proto2 supports the definition of enumeration types as enum.
Enums allow for the declaration of a set of named constants, each associated with a unique integer value.
This can be used for representing a fixed set of options or states within a message definition~\cite{protobuffer, proto2_doc}.

In the following, an example enum is shown and described. 
It represents the gender of a person and is defined as follows:

\begin{lstlisting}[style=protobufStyle, numbers=none]
	enum Gender {
		UNKNOWN = 0;
		MALE = 1;
		FEMALE = 2;
		DIVERSE = 3;
	}
\end{lstlisting}

Gender is the name of the enum and \texttt{UNKNOWN}, \texttt{MALE}, \texttt{FEMALE} and \texttt{DIVERSE} are the enum constants with the associated integer values $0$, $1$, $2$ and $3$.
It allows to represent the gender options unknown, male, female or diverse, providing a way to represent a fixed set of options or states.



\end{description}


	
\end{document}